### 2019-07-12 draft_charts.Rmd

* Quintiles are based on per-capita, price-adjusted, shared annuitized income with federal taxes, state taxes, payroll taxes and the Medicare surtax at age 70.
* Values are the mean of the different sources of income in each quintile.

Financial income = per-capita interest + per-capita dividends + per-capita rental income + per-capita IRA withdrawals

Other income = pcNotModel_Mean

```{r theme5}
incomes <- c("Other income", "Financial income", "DB pension income", "Earnings", "Social Security")
quintile <- c("Bottom quintile", "Second quintile", "Third quintile", "Fourth quintile", "Top quintile")

>>>>

* Quintiles are based on per-capita, price-adjusted, shared annuitized income with federal taxes, state taxes, payroll taxes and the Medicare surtax at age 70.

```{r theme5}
quintile <- c("Bottom quintile", "Second quintile", "Third quintile", "Fourth quintile", "Top quintile")
